A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-12-06 draft/paper2.tex
Minor typo corrections

% Version 0; preprint format; Outline of paper II by Song Huang
% Version 1; preprint format; Edited by Jenny Greene
% Version 2; preprint format; Edited by Song Huang
% Version 3; preprint format; Edited by Alexie Leauthaud
% Version 4; preprint format; Edited by Song Huang
% Version 5; preprint format; Edited by Jenny Greene and Song Huang

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    The $i$-band images from HSC survey reach ${\sim}4$ magnitudes deeper than SDSS 
    and enable us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking.  
    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter haloes. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$-$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the 
    mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
    Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc. 
    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    A key discovery in the last decade has been the dramatic structural transformation 
    of massive quiescent galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, 
    Cimatti2008, Damjanov2009, vanderWel2011, Szomoru2012, Patel2013} from 
    $z \approx 2$ to the present day. 
    These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
    galaxies (ETGs) need to increase their effective radii ($R_{\rm e}$) by a factor 
    of 2--4 over a time span of 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}). 
    This observational result spurred the development of the ``two-phase'' formation
    scenario for massive ETGs (e.g. \citealt{Oser2010, Oser2012}),
    in which galaxies form a compact central region at $z\sim 2$ through highly 
    dissipative processes (e.g. gas-rich mergers or cold gas-accretion;
    \citealt{Hopkins2008, Dekel2009}). 
    They subsequently assemble extended stellar haloes via dry mergers 
    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012} which can cause 
    significant size growth at late times. 
    An alternative explanation for size growth, progenitor bias, hypothesizes that 
    larger ETGs were quenched more recently, but this explanation is still under 
    active debate (e.g. \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
    Keating2015, Fagioli2016}).

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    \song{
    These observations are generally consistent with the two-phase formation scenario. 
    However, it is still not clear whether this promising picture can correctly 
    predict the connection between the stellar mass distributions in massive galaxies 
    and their dark matter haloes.
    }

    \song{
    Under the $\Lambda$CDM cosmology, The assembly of massive ETGs is intrinsically 
    tied to the hierarchal growth of their host dark matter haloes 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Hydrodynamic simulations suggest that the fraction of star accreted through 
    mergers (\textit{ex situ} component) in central galaxy increases with halo 
    mass (e.g. \citealt{Pillepich2017b}). 
    Although the major merger rate is not strong function of progenitor halo mass 
    (e.g. \citealt{Shankar2015}), minor mergers may still play a more important 
    role in the assembly of central galaxy of more massive dark matter halos 
    (e.g. \citealt{Guo2011, Yoon2017}). 
    As minor merger is more efficient at ``puffing up'' the outskirts of massive 
    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest the 
    structures of massive ETGs and the well-known stellar mass--effective radius 
    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should depend 
    on their ``environment''\footnote{There are multiple definitions of 
    ``environment'' in the literature.  
    In this work, we use ``environment'' and halo mass interchangeably.}
    (e.g. \citealt{Shankar2013, Shankar2014}). 
    However, evidence for the environment--dependence of \mstar{}--$R_{\rm e}$
    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
    but also see \citealt{Yoon2017}), while the results at higher redshift are 
    even more confusing (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}).
    }

	\song{
    Therefore, we think it requires deeper images of these massive galaxies to 
    better probe their outer stellar mass distributions and test these 
    predictions. 
    Unfortunately, this is observationally challenging since the stellar haloes 
    of massive galaxies can extend to $>100$ kpc (e.g.\citealt{Tal2011, DSouza2014}),
    and their surface brightness profiles decline rapidly with typical values of 
    $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and at $z\sim0.3$. 
    }
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
    showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
    massive galaxies on 100 kpc scales. 
    In this paper, we now investigate whether or not the large scatter in the outer 
    profiles of massive galaxies correlate with halo mass. 
    We conclusively show that the sizes and stellar haloes of massive central galaxies 
    depend on dark matter halo mass. 
    In other terms, we reveal the halo mass dependence of the mass-size relation 
    for massive ETGs.

    This paper is organized as follows. 
    In \S \ref{sec:data} we briefly introduce the sample selection and the data 
    reduction processes.  
    Please refer to \citet{hscMassiveI} for more technical details.
    Our main results are presented in \S \ref{sec:result} and discussed in 
    \S \ref{sec:discussion}. 
    \S \ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}. 
    We assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}). Halo mass is defined as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$). 
    As in \citet{hscMassiveI}, we do not attempt to decompose or distinguish any  
    potential ``intra-cluster'' 
    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these massive galaxies have very similar \mstar{} within a 10 kpc 
          elliptical aperture 
          ($11.2<\log_{10} (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates $R=$10 kpc.
          These galaxies are rank-ordered from top to bottom and from left to right 
          by their \mstar{} within a 100 kpc elliptical aperture which varies 
          from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
          At fixed ``inner'' mass (\minn{}), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies from dark matter haloes that are more massive 
          than ${\sim} 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          Left: halo mass dependence of galaxy profiles at fixed ``total'' stellar mass 
          (\mtot{}). 
          Right: halo mass dependence of galaxy profiles at fixed ``inner-mass'' 
          (\minn{}). Orange and red lines correspond to central galaxies living in 
          haloes with \logmh{} $\geq 14.2$. 
          Black and grey lines correspond to central galaxies living in haloes with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          Brown lines in the bottom panels show the relative difference between  
          two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
          Errors on the difference between the two profiles are also computed 
          via bootstrap.
          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial 
          signal. 
          We repeat this process 5000 times.  
          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
      \caption{
          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
          \nbcg{} (grey dots) galaxies. 
          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
          The red solid line shows the best fit mass-size relation for \rbcg{} and the 
          grey dashed line shows the best fit relation for \nbcg{}. 
          Shaded regions in lighter colors show the 1-$\sigma$ uncertainties
          from MCMC sampling.  
          The green dashed line shows the mass-size relation for nearby central 
          galaxies in massive groups from \citet{HCompany13}. 
          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
          both samples.
          }
      \label{fig:scaling_relation} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We use imaging data from the HSC internal data release 
    \texttt{S15B}, which is very similar to the Public Data Release 1 
    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
    the full depth in the Wide field. 
    The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
    The pixel scale of the reduced image is $0.168$\asec{}.
    We use $i$-band images for extracting surface brightness profiles. 
    HSC $i$-band images are typically 3--4 mag deeper than SDSS 
    (Sloan Digital Sky Survey; e.g. \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
    and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
    \song{
    And massive galaxies should experience little structural evolution and 
    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr of time span) 
    based on model prediction (e.g. \citealt{Shankar2015}).
    }

    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out surrounding neighbors and accounting for the subtraction of the 
    background light. 
    We use the broadband spectral energy distributions (SED) fitting code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using 
    five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. 
    We assume a \citet{Chabrier2003} IMF, the Flexible Stellar Population 
    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), the 
    \citet{Calzetti2000} extinction law, and a simple delayed-$\tau$ model for 
    star formation histories (SFH). 
    Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
    $\sim 100$ kpc and we integrate these profiles within elliptical isophotal
    apertures at different physical radii. 
    As explained in Paper~I, here we focus on the two following metric masses:

@@

        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use 
            as a proxy for the stellar mass of the \textit{in situ} stellar 
            component. 
            This is motivated both by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
            The value of 10 kpc that we quote here corresponds to the radius of the 
            major axis of the isophotal ellipse.

        \item stellar mass within 100 kpc (hereafter noted \mtot{}). 
            We use \mtot{} as a proxy of the ``total'' stellar mass. 
            In Paper~I we showed that \mtot{} recovers more light compared to 
            HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex 
            in magnitude.

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars, and reveal the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it more useful to display figures using the more 
   simple \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
   very similar \minn{} that have large range of \mtot{}. 
   We will use these two apertures masses to guide our comparisons of massive galaxies 
   as a function of environment.

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
    to help us construct a central galaxy sample.

    %Central galaxies are important to the study of galaxy-halo connection and follow 
    %stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.

>>>>

% Version 1; preprint format; Outline of paper II by Song Huang
% Version 2; preprint format; Edited by Jenny Greene
% Version 3; preprint format; Edited by Song Huang
% Version 4; preprint format; Edited by Alexie Leauthaud
% Version 5; preprint format; Edited by Song Huang
% Version 6; preprint format; Edited by Jenny Greene and Song Huang
% Version 7; preprint format; Edited by Susan Foster and Song Huang
% Version 8; preprint format; Edited by Alexie Leauthaud and Song Huang
% Version 9; preprint format; Edited by Song Huang (Comments from Felipe Ardilla and Christopher Bradshaw)

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to 
    reveal the halo mass dependence of the surface mass density profiles and outer 
    stellar envelopes of massive galaxies. 
    The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
    Sloan Digital Sky Survey and enable us to directly trace stellar mass distributions 
    to 100 kpc without requiring stacking.  
    We conclusively show that, at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter haloes. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the mass--size relation. 
    Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in 
    $R_{\mathrm{50}}$ at fixed \mtot{}. 
    Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc.  
    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    A key discovery in the last decade has been the dramatic structural transformation 
    of massive quiescent galaxies \citep[e.g.,][]{Trujillo2006, vanDokkum2008, 
    Cimatti2008, Damjanov2009, vanderWel2011, Szomoru2012, Patel2013} from 
    $z \approx 2$ to the present day. 
    These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
    galaxies (ETGs) need to increase their effective radii ($R_{\rm e}$) by a factor 
    of 2--4 over a time span of 10 Gyrs (e.g., \citealt{Newman2012, vdWel2014}). 
    This observational result spurred the development of the `two-phase' formation
    scenario for massive ETGs (e.g., \citealt{Oser2010, Oser2012}),
    in which galaxies form a compact central region at $z\sim 2$ through highly 
    dissipative processes (e.g., gas-rich mergers or cold gas-accretion;
    \citealt{Hopkins2008, Dekel2009}). 
    They subsequently assemble extended stellar haloes via dry mergers 
    \citep[e.g.,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which can cause 
    significant size growth at late times. 
    An alternative explanation for size growth, progenitor bias, hypothesizes that 
    larger ETGs were quenched more recently; but this explanation is still under 
    active debate (e.g., \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
    Keating2015, Fagioli2016}).

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
    Oh2017}), optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    \song{
    These observations are generally consistent with the two-phase formation scenario. 
    However, it is still not clear whether this picture correctly 
    predicts the connection between the stellar mass distributions in massive galaxies 
    and their dark matter haloes.}

    \song{In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
    tied to the hierarchical growth of their host dark matter haloes 
    (e.g., \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Hydrodynamic simulations suggest that the fraction of stars accreted through 
    mergers (the \textit{ex situ} component) in central galaxies increases with halo 
    mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
    The major merger rate is not a strong function of progenitor halo mass 
    (e.g., \citealt{Shankar2015}) but minor mergers rate should increase with 
    halo mass, hence play an important role in determining the structures of central 
    galaxies (e.g., \citealt{Guo2011, Yoon2017}). 
    Minor mergers are efficient at `puffing up' the outskirts of massive 
    galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
    Because the minor merger rate increases with halo mass, the 
    structures of massive ETGs and the well-known stellar mass--effective radius 
    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should 
    depend on their `environment'\footnote{There are multiple definitions of 
    `environment' in the literature. 
    In this work, we use `environment' and halo mass interchangeably.}
    (e.g., \citealt{Shankar2013, Shankar2014}). 
    However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
    but also see \citealt{Yoon2017}), and the results at higher redshift are 
    even more unclear (e.g., \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}).
    }

	\song{
    Deep images of massive galaxies can probe their outer stellar halos of massive 
    galaxies and test these predictions. 
    Unfortunately, this is observationally challenging since the stellar haloes 
    of massive galaxies can extend to $>100$ kpc (e.g., 
    \citealt{Tal2011, DSouza2014}), and their surface brightness profiles decline 
    rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and 
    at $z\sim0.3$. 
    }
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs and 
    showed that there is a large intrinsic scatter in the stellar haloes of
    massive galaxies on 100-kpc scales. 
    In this paper, we investigate whether the large scatter in the outer 
    profiles of massive galaxies correlates with halo mass. 
    We conclusively show that the sizes and stellar haloes of massive central 
    galaxies depend on dark matter halo mass. 
    In other words, we reveal the halo mass dependence of the mass--size relation 
    for massive ETGs.

    This paper is organized as follows. 
    In \S \ref{sec:data} we briefly introduce the sample selection and the data 
    reduction processes.  
    Please refer to \citet{hscMassiveI} for more technical details.
    Our main results are presented in \S \ref{sec:result} and discussed in 
    \S \ref{sec:discussion}. 
    Our summary and conclusions are presented in \S \ref{sec:summary}.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for galactic 
    extinction using calibrations from \citet{Schlafly11}. 
    We assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is denoted \mstar{} and has been derived using a Chabrier initial mass 
    function (IMF; \citealt{Chabrier2003}). Halo mass is defined as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$, where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$). 
    As in \citet{hscMassiveI}, we do not attempt to decompose or distinguish any  
    potential `intra-cluster' 
    component (ICL; e.g., \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-colour images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these massive galaxies have very similar \mstar{} within a 10-kpc 
          elliptical aperture 
          ($11.2<\log_{10} (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dashed-line circle at the top-left figure indicates $R=$10 kpc.
          These galaxies are rank-ordered from top to bottom and from left to right 
          by their \mstar{} within a 100-kpc elliptical aperture that varies 
          from $10^{11.2}\ M_{\odot}$ to $10^{11.7}\ M_{\odot}$. 
          At fixed `inner' mass (\minn{}), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies from dark matter haloes that are more massive 
          than ${\sim} 10^{14}\ M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We use imaging data from the HSC internal data release 
    \texttt{S15B}, which is very similar to the Public Data Release 1 
    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
    the full depth in the wide field. 
    The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
    The pixel scale of the reduced image is $0.168$\asec{}.
    We use $i$-band images for extracting surface brightness profiles. 
    HSC $i$-band images are typically 3--4 mag deeper than SDSS 
    (Sloan Digital Sky Survey; e.g., \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
    and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5, respectively). 
    \song{
    Massive galaxies should experience little structural evolution and 
    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
    based on model predictions (e.g., \citealt{Shankar2015}).
    }

    After carefully 
    masking out surrounding neighbors and accounting for the subtraction of the 
    background light, we derive $i$-band surface brightness profiles out to 100 kpc. 
    We use the broadband spectral energy distributions (SED) fitting code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using 
    five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. 
    We assume a \citet{Chabrier2003} IMF, the Flexible Stellar Population 
    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), the 
    \citet{Calzetti2000} extinction law, and a simple delayed-$\tau$ model for 
    star formation histories (SFH). 
    Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
    $\sim 100$ kpc, and we integrate these profiles within elliptical isophotal
    apertures at different physical radii. 
    As explained in Paper~I, we focus on the two following metric masses:

@@

        \item Stellar mass within 10 kpc (hereafter noted \minn{}), which we use 
            as a proxy for the stellar mass of the \textit{in situ} stellar 
            component. 
            This is motivated both by observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
            The value of 10 kpc that we quote here corresponds to the radius of the 
            major axis of the isophotal ellipse.

        \item Stellar mass within 100 kpc (hereafter noted \mtot{}). 
            We use \mtot{} as a proxy for the `total' stellar mass. 
            In Paper~I we show that \mtot{} recovers more light compared to 
            HSC \cmodel{} photometry with differences that can be a large as 0.2 dex 
            in magnitude.

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it useful to display figures using the simpler 
   \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a subsample of massive galaxies with very 
   similar \minn{} but show a large range of \mtot{}. 
   We use these two aperture masses to guide our comparison of massive galaxies 
   as a function of environment.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          \textbf{Left}: Halo mass dependence of galaxy \mden{} profiles at fixed 
          `total' stellar mass (\mtot{}). 
          \textbf{Right}: Halo mass dependence of galaxy \mden{} profiles at fixed 
          `inner-mass' (\minn{}). 
          In each plot, we match the two samples so that they share similar 
          distributions of mass and redshift (Appendix~\ref{app:match}).
          We use $R^{1/4}$ as $x$--axis to provide a balanced view of both the central 
          and outer regions of the galaxy.
          Orange and red lines correspond to central galaxies living in 
          haloes with \logmh{} $\geq 14.2$. 
          Black and grey lines correspond to central galaxies living in haloes with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies, while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          Brown lines in the bottom panels show the relative difference between  
          the two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
          Errors in the difference between the two profiles are also computed 
          via bootstrap.
          The grey-shaded regions show a Monte Carlo test to assess how likely it is to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey-shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial 
          signal. 
          We repeat this process 5000 times.  
          The dark grey--shaded region (light grey--shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
      \caption{
          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
          \nbcg{} (grey dots) galaxies. 
          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
          The red solid line shows the best-fitting mass--size relation for \rbcg{} and the 
          grey dashed line shows the best-fitting relation for \nbcg{}. 
          Shaded regions in lighter colours show the 1-$\sigma$ uncertainties
          from Markov chain Monte Carlo (MCMC) sampling.  
          \song{
          The green dashed line shows the mass--size relation for $z<0.09$ central 
          galaxies in massive groups from \citet{HCompany13}. 
          And the cyan dashed line represents the mass--size relation for 
          $0.2<z<0.5$ ETGs in groups from the COSMOS survey provided by 
          \citet{HueartasCompany2013b}.
          }
          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
          \rbcg{} and \nbcg{} galaxies, along with the best-fitting scaling relations for 
          both samples.
          }
      \label{fig:scaling_relation} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes -- so-called `central' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
    to help us construct two central galaxy samples: one for high mass haloes, and 
    one for low mass haloes.
